\documentclass[12pt, class=article, crop=false]{standalone}
\usepackage[subpreambles=true]{standalone}
\usepackage[T1]{fontenc} % for font setting
\usepackage{newtxtext,newtxmath}
\usepackage{import,
            graphicx,
            parskip,
            url,
            amsmath,
            wrapfig,
            fancyhdr}
\usepackage[most]{tcolorbox}
\usepackage[top=2.54cm, bottom=2.54cm, left=2.54cm, right=2.54cm, marginparwidth=2cm]{geometry}%set margin
\usepackage[sort&compress]{natbib}
\setcitestyle{square}
\setcitestyle{comma}
\usepackage[font={sf, small}, labelfont={bf, small}]{caption}

\tcbuselibrary{breakable}
\bibliographystyle{bibstyle}
\graphicspath{{images/}}

% header
\pagestyle{fancy}
\fancyhead[L]{Key Personnel}
\fancyhead[R]{}

\begin{document}

\section*{Key Personnel}

\subsection*{PD: Akira Terui, University of North Carolina at Greensboro (UNCG)}
PD Terui will serve as the lead of this project, synthesizing the products from each supporting objective.
Terui will also be responsible for overseeing and advising all aspects of statistical analysis in the project and for mentoring and working with a postdoc (TBD) who is expected to support the data analysis in Supporting Objectives 2 \& 3.
He has a strong track record in population and community ecology with developments of novel theoretical and statistical tools.

\subsection*{Co-PD: Amy T. Hansen, University of Kansas (KU)}
The KU researcher, Co-PD Hansen will hold primary responsibility for all tasks outlined under Supporting Objective 1: Quantify the impact of mitigation practices (cover crops, riparian buffer strips, and wetlands) on surface water quality.
The research activity of the KU postdoctoral researcher will also directly support Objective 1.
Both KU researchers will be actively engaged in all stages of the project and will contribute intellectually to the conceptualization and implementation of the proposed work.

\subsection*{Co-PD: Jacques C. Finlay, University of Minnesota (UM)}
CO-PD Jacques Finlay will serve as lead PI, overseeing overall project objectives and managing project personnel.
Finlay’s current research is focused on understanding water quality impacts and identifying solutions to reduce them in human dominated landscapes of the Midwest, and includes experimental, comparative and modeling studies at scales ranging from plot, river, and whole watershed scales.
He has published over 30 research papers related to water quality, restoration, and management in the Midwest.
Finlay will serve as the Contact PI for the project.

\subsection*{Co-PD: Christine L. Dolph, UM}
CO-PD Christy Dolph will contribute to the three specified project objectives by 1) assisting with the assembly of geospatial datasets needed for project modelling; 2) assisting with the assembly of fish taxonomic data and contributing to project statistical modelling efforts; 3) advising on aspects of fish ecology necessary for models that meaningfully link climate, conservation and biodiversity; 4) interfacing between the proposed project and other currently-funded projects (one funded by USEPA, two funded by USDA-CEAP) with synergistic objectives; and 5) authoring peer-reviewed research for publication.
Dolph is a researcher in the Department of Ecology, Evolution and Behavior at the University of Minnesota. She is an expert in stream and river ecology, and has worked extensively with biological, physical and chemical datasets to examine relationships between land use, hydrology, water quality and stream health for the Midwestern United States.
She has prior experience coordinating large multi-institution, interdisciplinary projects and collecting and curating large publicly-available datasets.

\subsection*{Co-PD: Bryan Piazza, The Nature Conservancy (TNC)}
CO-PD Bryan Piazza will be responsible for managing TNC's contribution to this project and ensuring continuity with the NRCS CEAP Wildlife project, tools, and stakeholder constituencies.
He will contribute to all aspects of TNC’s contribution to this project and will coordinate this project with other TNC and stakeholder efforts focused on improving water and aquatic habitat quality.

\subsection*{Co-PD: Katie Kennedy, TNC}
CO-PD Katie Kennedy will be responsible for stakeholder outreach and, as such, will contribute to all aspects of this project.
She will manage TNC’s stakeholder advisory team that we built for the CEAP-Wildlife project and ensure that this current project advances conservation on the ground through the stakeholder outreach and integration of scientific results from this project into TNC’s CEAP tool. 

\subsection*{Co-PD: David Harlan, TNC}
CO-PD David Harlan will contribute to all aspects of this project and will direct the integration of project data into TNC’s CEAP tool and any re-branding that may occur. He will also support the stakeholder outreach to ensure that the scientific information from this project improves the delivery of information to users in an understandable and useful way. 

\end{document}
